---
title: "QC"
author: "`r Sys.getenv('USER')`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_download: true
    code_folding: hide
    toc: true
    toc_float: true
    fig_caption: true
params:
    outdir: "out/reservoir_phase1"
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE)
library(tidyverse)
library(BiocParallel)
BiocParallel::register(BiocParallel::MulticoreParam(workers=6,progress=TRUE))
library(patchwork)

fct_reorder2_hclust <- function(.f, .y, .value,hclust.method="ward.D2") {
  wide <- tibble(f = .f, y = .y, value = .value) %>%
    pivot_wider(names_from = f, values_from = value,values_fill = 0) %>%
    column_to_rownames("y") %>%
    as.matrix() %>%
    t()
  h <- hclust(dist(wide),method=hclust.method)
  fct_relevel(.f,h$labels[h$order])
}
```

```{r}
source("notebooks/lib_typing.R")
```



# Load sample-sheet associated data {.tabset}

- Load samplesheet

```{r include=FALSE}
# Load the sample sheet
ss <- openxlsx::read.xlsx("data/sample_sheet_reservoir_phase1_2025-05-21.xlsx","barcodes") |>
 	mutate(assembly_id = str_glue("r{run_id}b{bc}"))
db <- db_load(ss,"out/data_reservoir_phase1")
res_pheno <- readxl::read_xlsx("data/resfinder_category.xlsx")
```


```{r}
db$species <- db$species |>
	left_join(read_tsv("local/species_profiler/notebooks/db_tax.tsv") |> select(assembly_acc,species_name,genus_name),by="assembly_acc") |>
	mutate(species_name=factor(species_name),genus_name=factor(genus_name))
db$SPECIES <- db$species |>
	group_by(assembly_id) |>
	slice_max(ANI,n=1) |>
	right_join(select(ss,assembly_id))
db$contigs <- db$contigs |>
	left_join(
		as_tibble(db$plasmidfinder) |> 
			group_by(contig_id=seqnames) |> 
			summarize(plasmid_types = list(plasmid_type))
	) |>
	left_join(
		as_tibble(db$resfinder) |> 
			group_by(contig_id=seqnames) |> 
			summarize(resistances = list(resistance_name))
	) |>
	mutate(is_plasmid = (contig_length<=500000) & lengths(plasmid_types)>0)
```




## Summary
```{r,message=TRUE}
message(str_glue("Number of sample/assembly: {nrow(ss)}"))
message(str_glue("Number of contig: {nrow(db$contigs)}"))
```





```{r io, echo=FALSE}
dir.create(fs::path(params$outdir))
saveRDS(ss,fs::path(params$outdir,"ss.rds"))
saveRDS(db,fs::path(params$outdir,"db.rds"))
```


# Species
```{r,fig.height=2.5, fig.width=6}
db$SPECIES |>
	left_join(ss,by="assembly_id") |>
	left_join(db$mlst,by="assembly_id") |>
	mutate(mlst_type=replace_na(mlst_type,"?") |> fct_recode("?"="Unknown")) |>
	group_by(source,genus_name,species_name) |>
	count() |>
	arrange(species_name) |>
	rowid_to_column() |>
	ggplot(aes(y=species_name,x=n)) +
		facet_grid(genus_name~source,space="free",scales = "free") + 
		geom_col(color="black",fill="lightblue") +
		geom_text(aes(label=n),position = position_stack(vjust=0.5),size=3,angle=0) +
		theme_bw() +
		theme(legend.position = "none")+
		theme(
			panel.spacing = unit(0,"mm"),
			panel.grid = element_blank(),
			strip.text.y = element_text(angle = 0),
			strip.placement = "outside"
		) + 
		xlab("Num. sample") + ylab("")
```


# ST
```{r,fig.height=4, fig.width=8}
db$SPECIES |>
	left_join(ss,by="assembly_id") |>
	left_join(db$mlst,by="assembly_id") |>
	mutate(mlst_type=replace_na(mlst_type,"?") |> fct_recode("?"="Unknown")) |>
	group_by(source,genus_name,species_name,mlst_type) |>
	count() |>
	arrange(species_name,mlst_type) |>
	rowid_to_column() |>
	ggplot(aes(y=species_name,x=n,fill=mlst_type)) +
		facet_grid(genus_name~source,space="free",scales = "free") + 
		geom_col(color="black") +
		geom_text(aes(label=mlst_type),position = position_stack(vjust=0.5),size=3,angle=90) +
		theme_bw() +
		theme(legend.position = "none")+
		theme(
			panel.spacing = unit(0,"mm"),
			panel.grid = element_blank(),
			strip.text.y = element_text(angle = 0),
			strip.placement = "outside"
		) + 
		xlab("Num. sample") + ylab("")
```




# Resistances

```{r fig.height=10, fig.width=2.7}
ss |>
	left_join(db$SPECIES,by="assembly_id") |>		
	left_join(db$mlst,by="assembly_id") |>
	left_join(db$contigs,by="assembly_id") |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(assembly_id=str_glue("{cmu_id} ({assembly_id})")) |>
	ungroup() |>
	distinct(source,assembly_id,resistance_name,res_subgroup) |>
	mutate(assembly_id = fct_reorder2_hclust(assembly_id,resistance_name,rep_along(assembly_id,1),hclust.method = "complete")) |>
	filter(!is.na(res_subgroup)) |>
	ggplot(aes(x=resistance_name,y=assembly_id)) + 
		facet_grid(.~res_subgroup,space="free",scales="free") +
		scale_y_discrete(drop=FALSE) +
		geom_tile(fill="black") + 
		theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1)) + 
		ylab("sample") + xlab("")
```



```{r fig.height=4, fig.width=4}
ss |>
	left_join(db$SPECIES,by="assembly_id") |>		
	left_join(db$mlst,by="assembly_id") |>
	left_join(db$contigs,by="assembly_id") |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	left_join(res_pheno,by="resistance_name") |>
	group_by(assembly_id) |>
	summarize(BetaLactam=any(res_group=="Beta-lactam"),Carba=any(res_subgroup=="Carba"),ESBL=any(res_subgroup=="ESBL")) |>
	mutate(across(!assembly_id,~replace_na(.,FALSE))) |>
	column_to_rownames("assembly_id") |>
	gplots::venn()
```


```{r fig.height=4, fig.width=4}
ss |>
	left_join(db$SPECIES,by="assembly_id") |>		
	left_join(db$mlst,by="assembly_id") |>
	left_join(db$contigs,by="assembly_id") |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	left_join(res_pheno,by="resistance_name") |>
	group_by(assembly_id) |>
	select(assembly_id,source,resistance_name,res_subgroup) |>
	filter(!is.na(res_subgroup)) |>
	mutate(true=TRUE) |>
	pivot_wider(id_cols=c(source,assembly_id),names_from = resistance_name,values_from = true,values_fn = any) |>
	ungroup() |>
	mutate(across(!c(source,assembly_id),~replace_na(.,FALSE)+0)) |>
	as.data.frame() |>
	UpSetR::upset(nsets = 6) 
```




```{r fig.height=20, fig.width=6}
res_count <- select(as.data.frame(db$res),contig_id=seqnames,resistance_name) |>
	inner_join(select(db$contigs,contig_id,assembly_id)) |>
	left_join(ss,by="assembly_id") |>	
	group_by(resistance_name,source) |>
	summarise(n_assembly = n_distinct(assembly_id)) |>
	ungroup() |>
	arrange(desc(resistance_name)) |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(res_group=replace_na(res_group,"Other") |> fct_relevel("Other",after=+Inf)) |>
	mutate(res_subgroup=replace_na(res_subgroup,"-") |> fct_relevel("-",after=+Inf)) |>
	mutate(resistance_name=fct_reorder(resistance_name,n_assembly,sum))

ggplot(res_count,aes(y=resistance_name,x=n_assembly)) +
	facet_grid(res_group+res_subgroup~source,scales="free_y",space="free_y") +
	geom_col(fill="lightblue",color="black") +
	geom_text(aes(label=n_assembly),position = position_stack(vjust=0.5),size=3) +
	theme_bw() +
	ggtitle("Resistance Profile")
```


## Detail

```{r fig.height=25, fig.width=20}
ss |>
	left_join(db$SPECIES,by="assembly_id") |>		
	left_join(db$mlst,by="assembly_id") |>
	left_join(db$contigs,by="assembly_id") |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	unnest_longer(plasmid_types,values_to = "plasmid_type",keep_empty = TRUE) |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(assembly_id=str_glue("{cmu_id} ({assembly_id})")) |>
	ungroup() |>
	distinct(source,assembly_id,contig_id,is_plasmid,resistance_name,res_subgroup) |>
	mutate(contig_id = fct_reorder2_hclust(contig_id,resistance_name,rep_along(contig_id,1),hclust.method = "complete")) |>
	ggplot(aes(x=resistance_name,y=contig_id)) + 
		facet_grid(source+assembly_id~res_subgroup,space="free",scales="free") +
		#scale_y_discrete(drop=FALSE) +
		geom_tile(aes(fill=is_plasmid)) + 
		theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1)) + 
		theme(strip.text.y = element_text(angle = 0)) +
		theme(panel.spacing = unit(0,"mm"),panel.border = element_rect(color="black",fill = NA)) +
		theme(legend.position="top") +
		ylab("contig") + xlab("")
```

```{r fig.height=15, fig.width=15}
select(as.data.frame(db$res),contig_id=seqnames,resistance_name) |>
	inner_join(select(db$contigs,contig_id,assembly_id)) |>
	group_by(resistance_name,assembly_id) |>
	summarize(n=n_distinct(contig_id)) |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(res_group=replace_na(res_group,"Other") |> fct_relevel("Other",after=+Inf)) |>
	mutate(res_subgroup=replace_na(res_subgroup,"-") |> fct_relevel("-",after=+Inf)) |>
	ungroup() |>
	left_join(ss,by="assembly_id") |>
	mutate(assembly_id=fct_reorder2_hclust(assembly_id,resistance_name,n)) |>
	mutate(resistance_name=fct_reorder2_hclust(resistance_name,assembly_id,n)) |>
	ggplot(aes(y=resistance_name,x=assembly_id)) +
		facet_grid(res_group+res_subgroup~source,scales="free",space="free") +
		geom_tile() + 
		theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1))
```

# Resistances & Species
```{r fig.height=20, fig.width=8}
res_count <- select(as.data.frame(db$res),contig_id=seqnames,resistance_name) |>
	inner_join(select(db$contigs,contig_id,assembly_id)) |>
	left_join(ss,by="assembly_id") |>	
	left_join(db$mlst,by="assembly_id") |>
	left_join(db$SPECIES,by="assembly_id") |>
	mutate(mlst_type=replace_na(mlst_type,"?") |> fct_recode("?"="Unknown")) |>
	group_by(resistance_name,source,species_name) |>
	summarise(n_assembly = n_distinct(assembly_id)) |>
	ungroup() |>
	arrange(desc(resistance_name)) |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(res_group=replace_na(res_group,"Other") |> fct_relevel("Other",after=+Inf)) |>
	mutate(res_subgroup=replace_na(res_subgroup,"-") |> fct_relevel("-",after=+Inf)) |>
	mutate(resistance_name=fct_reorder(resistance_name,n_assembly,sum))

ggplot(res_count,aes(y=resistance_name,x=n_assembly,fill=species_name)) +
	facet_grid(res_group+res_subgroup~source,scales="free_y",space="free_y") +
	geom_col(color="black") +
	geom_text(aes(label=n_assembly),position = position_stack(vjust=0.5),size=3) +
	theme_bw() +
	ggtitle("Resistance Profile") +
	theme_bw() +
	theme(legend.position = "top")+
	theme(
		panel.spacing = unit(0,"mm"),
		panel.grid = element_blank(),
		strip.text.y = element_text(angle = 0),
		strip.placement = "outside"
	)
	
```


# Resistances & plasmid
```{r fig.height=15, fig.width=6.5}
ss |>
	left_join(db$SPECIES,by="assembly_id") |>		
	left_join(db$mlst,by="assembly_id") |>
	left_join(db$contigs,by="assembly_id") |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	unnest_longer(plasmid_types,values_to = "plasmid_type",keep_empty = TRUE) |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(assembly_id=str_glue("{cmu_id} ({assembly_id})")) |>
	ungroup() |>
	filter(!is.na(res_subgroup)) |>
	distinct(source,assembly_id,contig_id,is_plasmid,resistance_name,res_subgroup) |>
	mutate(contig_id = fct_reorder2_hclust(contig_id,resistance_name,rep_along(contig_id,1),hclust.method = "complete")) |>
	ggplot(aes(x=resistance_name,y=contig_id)) + 
		facet_grid(source+assembly_id~res_subgroup,space="free",scales="free") +
		#scale_y_discrete(drop=FALSE) +
		geom_tile(aes(fill=is_plasmid)) + 
		theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1)) + 
		theme(strip.text.y = element_text(angle = 0)) +
		theme(panel.spacing = unit(0,"mm"),panel.border = element_rect(color="black",fill = NA)) +
		theme(legend.position="top") +
		ylab("contig") + xlab("")
```


# Assembly statistics 

## Overview
```{r fig.height=3, fig.width=5}
db$contigs |>
	group_by(assembly_id) |>
	summarize(num_contig = n(),assembly_len=sum(contig_length)) |>
	left_join(db$SPECIES,by="assembly_id") |>
	ggplot(aes(x=num_contig,y=assembly_len)) + 
		geom_point(aes(color=genus_name)) + 
		ggrepel::geom_text_repel(aes(label=assembly_id),size=2) + 
	  scale_y_continuous(labels = scales::label_number(scale_cut = scales::cut_short_scale())) +
		theme_bw() + scale_x_log10()
```


## Detailed {.tabset}


### Color by genus
```{r fig.height=15, fig.width=7}
db$contigs |>
	left_join(select(ss,assembly_id,run_id)) |>
	left_join(db$SPECIES)	|>
	mutate(assembly_id = fct_reorder(assembly_id,contig_length,sum)) |>
	mutate(contig_id = fct_reorder(contig_id,contig_length,sum)) |>
	ggplot() + 
		facet_grid(run_id~.,space = "free_y",scales="free_y") +
		geom_col(aes(x=contig_length,y=assembly_id,group=contig_id,fill=genus_name),color="black",position="stack") + 
		scale_x_continuous(position="top",labels = scales::label_number(scale_cut = scales::cut_short_scale())) +
		theme_bw() + theme(legend.position="top")
```


### Color by plasmid

 Here is a plasmid is defined as a <=500kb sequence with an Inc detected

```{r fig.height=15, fig.width=7}
db$contigs |>
	left_join(select(ss,assembly_id,run_id)) |>
	mutate(assembly_id = fct_reorder(assembly_id,contig_length,sum)) |>
	mutate(contig_id = fct_reorder(contig_id,contig_length,sum)) |>
	ggplot() + 
		facet_grid(run_id~.,space = "free_y",scales="free_y") +
		geom_col(aes(x=contig_length,y=assembly_id,group=contig_id,fill=is_plasmid),color="black",position="stack") + 
		scale_x_continuous(position="top",labels = scales::label_number(scale_cut = scales::cut_short_scale())) +
		theme_bw() + theme(legend.position="top") + labs(fill="plamid")
```









# Plasmidfinder typing results 


## Inc types overview
```{r fig.height=9, fig.width=5}
select(as.data.frame(db$plasmidfinder),contig_id=seqnames,plasmid_type) |>
	inner_join(select(db$contigs,contig_id,assembly_id,is_plasmid)) |>
	right_join(select(ss,assembly_id)) |>
	filter(is_plasmid) |>
	group_by(plasmid_type) |>
	summarise(n_assembly = n_distinct(assembly_id)) |>
	ungroup() |>
	mutate(plasmid_type=fct_reorder(plasmid_type,n_assembly,mean)) |>
	ggplot(aes(y=plasmid_type,x=n_assembly)) +
		geom_col(fill="lightblue",color="black") +
		geom_text(aes(label=n_assembly),position = position_stack(vjust=0.5),size=3) +
		scale_x_continuous(position="top") +
		theme_bw() +
		ggtitle("Overall Plasmid Type Profile") + xlab("Number of assembly")
```

## Plasmid size
```{r}
db$contigs |>
	filter(is_plasmid) |>
	mutate(has_resistance=lengths(resistances)>0) |>
	ggplot(aes(x=contig_length,y=GC,shape=tag_topology,size=lengths(plasmid_types),color=has_resistance)) +
		geom_point() + 
		scale_x_continuous(limits=c(0,500e3),oob=scales::squish,labels = scales::label_number(scale_cut = scales::cut_short_scale())) + 
		scale_y_continuous(label=scales::percent) + 
		ggtitle("Size, GC content and topology of plasmids") + 
		labs(shape="Topology",color="Carry resistance",size="Num. Inc") +
		xlab("Contig size") + ylab("GC content")
```




## Compatibility
```{r fig.height=7, fig.width=8}
select(as.data.frame(db$plasmidfinder),contig_id=seqnames,plasmid_type) |>
	inner_join(select(db$contigs,contig_id,assembly_id)) %>%
	full_join(.,.,by="assembly_id") |>
	filter(contig_id.x != contig_id.y) |>
	group_by(plasmid_type.x,plasmid_type.y) |>
	summarize(n_assembly=n_distinct(assembly_id)) |>
	arrange(desc(n_assembly)) |>
	ungroup() |>
	mutate(plasmid_type.x=fct_reorder2_hclust(plasmid_type.x,plasmid_type.y,n_assembly)) |>
	mutate(plasmid_type.y=fct_reorder2_hclust(plasmid_type.y,plasmid_type.x,n_assembly)) |>	
	ggplot(aes(x=plasmid_type.x,y=plasmid_type.y,fill=n_assembly)) +
		geom_tile() +
		theme_bw() + 
		coord_equal() + theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1))
```










# Plasmids and Resistance {.tabset}

## Overview
```{r fig.height=9, fig.width=5}
db$contigs |>
	left_join(ss,by="assembly_id") |>
	filter(is_plasmid) |>
	select(assembly_id,contig_id,contig_length,GC,plasmid_types,resistances,source) |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	group_by(resistance_name,source) |>
	summarize(n_assembly=n_distinct(assembly_id)) |>
	ungroup() |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(res_group=replace_na(res_group,"Other") |> fct_relevel("Other",after=+Inf)) |>
	mutate(res_subgroup=replace_na(res_subgroup,"-") |> fct_relevel("-",after=+Inf)) |>
	mutate(resistance_name=fct_reorder(resistance_name,n_assembly,sum)) |>
	ggplot(aes(y=resistance_name,x=n_assembly)) + 
		facet_grid(res_group+res_subgroup~source,scales="free",space="free") +
		geom_col(fill="lightblue",color="black") +
		geom_text(aes(label=n_assembly),position = position_stack(vjust=0.5),size=3) + 
		ggtitle("Plasmid resitances") + xlab("Num. sample with a resistant plasmid")
```

## Color by species of origin
```{r fig.height=10, fig.width=7}
db$contigs |>
	left_join(ss,by="assembly_id") |>
	filter(is_plasmid) |>
	select(assembly_id,contig_id,contig_length,GC,plasmid_types,resistances,source) |>
	left_join(db$mlst,by="assembly_id") |>
	left_join(db$SPECIES,by="assembly_id") |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	group_by(resistance_name,source,species_name) |>
	summarize(n_assembly=n_distinct(assembly_id)) |>
	ungroup() |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(res_group=replace_na(res_group,"Other") |> fct_relevel("Other",after=+Inf)) |>
	mutate(res_subgroup=replace_na(res_subgroup,"-") |> fct_relevel("-",after=+Inf)) |>
	mutate(resistance_name=fct_reorder(resistance_name,n_assembly,sum)) |>
	ggplot(aes(y=resistance_name,x=n_assembly,fill=species_name)) + 
		facet_grid(res_group+res_subgroup~source,scales="free",space="free") +
		geom_col(,color="black") +
		geom_text(aes(label=n_assembly),position = position_stack(vjust=0.5),size=3) + 
		ggtitle("Plasmid resitances") + xlab("Num. sample with a resistant plasmid") +
	theme_bw() +
	theme(legend.position = "top")+
	theme(
		panel.spacing = unit(0,"mm"),
		panel.grid = element_blank(),
		strip.text.y = element_text(angle = 0),
		strip.placement = "outside"
	)
```




# Carba+ESLB plasmids map

```{r fig.height=8, fig.width=25}
roi <- filter(res_pheno,res_subgroup %in% c("Carba","ESBL")) |> pull(resistance_name)
pl_contigs <- db$contigs |>
	filter(is_plasmid) |>
	filter(map_lgl(resistances,~any(. %in% roi))) |>
	left_join(ss,by="assembly_id") |>
	left_join(db$SPECIES,by="assembly_id") |>
	left_join(db$mlst,by="assembly_id") |>
	mutate(mlst_type=replace_na(mlst_type,"?") |> fct_recode("?"="Unknown")) |>	
	ungroup() |>
	mutate(contig_id=fct_reorder(contig_id,contig_length,mean))
	

p1 <- ggplot(pl_contigs,aes(y=contig_id,x=contig_length)) + 
		geom_col(fill="grey") + 
		scale_y_discrete(drop=FALSE) + 
		ylab("plasmid")

p2 <- ggplot(pl_contigs,aes(y=contig_id,x=species_name)) + 
		geom_tile(fill="grey") + 
		geom_text(aes(label=mlst_type),size=3) +
		scale_y_discrete(drop=FALSE) + ylab("") +
		theme(axis.text.x=element_text(angle=30,hjust = 1,vjust=1),panel.spacing = unit(0,"mm"))

p3 <- ggplot(pl_contigs,aes(y=contig_id,x=source)) + 
		geom_tile(fill="grey") +
		scale_y_discrete(drop=FALSE) + ylab("") +
		theme(axis.text.x=element_text(angle=30,hjust = 1,vjust=1),panel.spacing = unit(0,"mm"))

p4 <- pl_contigs |>
	unnest_longer(resistances,values_to = "resistance_name") |>
	distinct(contig_id,resistance_name) |>
	ungroup() |>
	left_join(res_pheno,by="resistance_name") |>
	mutate(res_group=replace_na(res_group,"Other") |> fct_relevel("Other",after=+Inf)) |>
	mutate(res_subgroup=replace_na(res_subgroup,"-") |> fct_relevel("-",after=+Inf)) |>
	mutate(resistance_name=fct_reorder2_hclust(resistance_name,contig_id,rep_along(contig_id,1))) |>
	ggplot(aes(y=contig_id,x=resistance_name)) + 
		facet_grid(~res_group+res_subgroup,space="free_x",scales="free_x") +
		geom_tile(fill="grey") +
		scale_y_discrete(drop=FALSE) + ylab("")+
		theme(axis.text.x=element_text(angle=30,hjust = 1,vjust=1),panel.spacing = unit(0,"mm"))

p5 <- pl_contigs |>
	unnest_longer(plasmid_types,values_to = "plasmid_type") |>
	distinct(contig_id,plasmid_type) |>
	ungroup() |>
	mutate(plasmid_type=fct_reorder2_hclust(plasmid_type,contig_id,rep_along(contig_id,1))) |>
	ggplot(aes(y=contig_id,x=plasmid_type)) + 
		geom_tile(fill="grey") +
		scale_y_discrete(drop=FALSE) + ylab("")+
		theme(axis.text.x=element_text(angle=30,hjust = 1,vjust=1),panel.spacing = unit(0,"mm"))


p1 + p2 + p3 + p4 + p5 + plot_layout(axes="collect",width=c(3,3,1,16,8))
```


